---
title: "Master - Detail Report"
format:
  typst:
    margin:
      x: 0.8cm
      y: 0.8cm
    mainfont: "Helvetica"
execute:
  echo: false
  warning: false
  message: false
---

```{=typst}
#set text(  font: "Helvetica",  size: 9pt)
```

```{r}
#| label: load-packages
#| echo: true
#| error: true
pacman::p_load(tidyverse, knitr, kableExtra, gt, tinytable, pander)

mtcars %>% head() %>% glimpse()

mtcars %>% head()

cat("## GT Table\n")

mtcars %>% head(30) %>% gt() %>%   opt_table_font(   font = "Helvetica",   add = FALSE  )

cat("## Kable Table\n")
mtcars %>% head(30) %>% kable()

cat("## Tinytable\n")
mtcars %>% head(30) %>% tinytable::tt(theme="grid", fontsize = 0.8)
#https://rapporter.github.io/pander/
cat("## Pander\n")
mtcars %>% head(30) %>% pander::pandoc.table(style='simple', split.tables = Inf, justify = "center", caption = "Pander Table")

cat("```{=typst}\n")
cat("== Tinytable Output\n")
cat("This will not work in Typst, but it works in R Markdown, it needs results asis.\n")
cat("```\n")

master_detail <- mtcars %>% rownames_to_column("car") %>% select(car, mpg, cyl, disp, hp, drat, wt, qsec, vs, am, gear, carb) %>% mutate(ser= row_number(), .by=gear) %>% group_by(gear) %>% summarise(n=n(), avgMPG = mean(mpg, na.rm=T), details = list(cur_data_all()), .groups = "drop") %>% select(gear, n, avgMPG, details)
#master_detail %>% tt()
typst_escape <- function(x) {
  x <- as.character(x)
  x[is.na(x)] <- ""
  x <- gsub("\\\\", "\\\\\\\\", x)
  x <- gsub("\\[", "\\\\[", x)
  x <- gsub("\\]", "\\\\]", x)
  x
}

```

```{r}
#| results: asis
#| echo: true
#| label: report-master-detail
for (i in seq_len(nrow(master_detail))) {
  gear_val <- master_detail$gear[i]
  n_val <- master_detail$n[i]
  avgMPG_val <- round(master_detail$avgMPG[i], 2)
  detail_tbl <- master_detail$details[[i]]

  cat("```{=typst}\n")
  cat("= Master Section\n")
  cat("#v(6pt)\n")
  cat("#text(weight: \"bold\")[Gear: ", gear_val, " | Count: ", n_val, " | Avg MPG: ", avgMPG_val, "]\n", sep = "")
  cat("== Detail Section\n")
  cat("#v(3pt)\n")
  cat("#table(\n")
  cat(" columns: (1fr, 1fr, 1fr, 1fr, 1fr), stroke: 0.4pt + black, inset: 2pt, align: center + horizon,\n")

  headers <- c('carname', 'mpg','cyl', 'hp', 'wt')

  for (h in headers) {
    cat("  [#text(weight: \"bold\")[", h, "]],\n", sep = "")
  }

    for (j in seq_len(nrow(detail_tbl))) {
    cat("  [", typst_escape(detail_tbl$car[j]), "],\n", sep = "")
    cat("  [", typst_escape(detail_tbl$mpg[j]), "],\n", sep = "")
    cat("  [", typst_escape(detail_tbl$cyl[j]), "],\n", sep = "")
    cat("  [", typst_escape(detail_tbl$hp[j]), "],\n", sep = "")
    cat("  [", typst_escape(detail_tbl$wt[j]), "],\n", sep = "")
    }
    cat(")\n")
 
    cat("```\n")
}
```


### Long Report - 1
```{r}
#| results: asis
#| echo: true
library(tinytable)
iris %>% head(60) %>% mutate(ser= row_number()) %>% select(ser, everything()) %>% tinytable::tt() |>  tinytable::style_tt(fontsize = .8) |>  tinytable::theme_typst(figure = FALSE, multipage=TRUE)
```

### Long Report - 2
```{r, results='asis'}
#| echo: true
library(gt)
iris %>% head(60) %>% gt() %>% opt_table_font(font = "Helvetica", size = px(12) )
```

### Long Report in 1 Page (IRIS)
```{=typst}
//#set page(  width: 29.7cm,  height: 21cm,  margin: 0.5cm)
#set text(size: 8pt)
#set par(leading: 0.75em)
#set text( font: "Arial",  size: 9pt)
```
```{r}
#| label: tbl-iris
#| output: asis
#| echo: true

library(tinytable)

iris %>%  head(50) %>%  tinytable::tt(width = 0.95) %>%  style_tt(fontsize = .7) %>%  theme_typst( figure = FALSE,    multipage = FALSE  )

```


### Tiny Table as Image
```{r}
#| label: tbl-compact-image
#| fig-width: 7
#| fig-height: 11
#| out-width: "100%"
#| out-height: "100%"
#| echo: true

library(knitr)
library(tinytable)

dir.create("assets", showWarnings = FALSE)
png_path <- file.path("assets", "iris.png")

tab <- mtcars %>% head(30) %>% tinytable::tt() |>  tinytable::theme_grid() |>  tinytable::style_tt(line="lrtb", line_color='black', line_width=.1, fontsize = .7)
tinytable::save_tt(  tab,  output = png_path,  overwrite = TRUE)
#knitr::include_graphics(png_path)
```

### This is image of TT Table
```{=typst}
#align(center)[  #image( "assets/iris.png", width: 70%, height: 60%,  fit: "contain" )]
```
::: {.callout-note}
This is demo report
:::