---
title: "Motor Trend Car Road Tests Analysis"
date: last-modified
---

## Introduction
This website displays performance attributes of various automobile models from the classic `mtcars` dataset. 

::: {.callout-note}
This entire site is dynamically generated using Quarto and R.
:::

## Fuel Efficiency vs. Weight
Let's look at how vehicle weight affects miles per gallon (MPG). 

```{r}
#| label: plot-mpg
#| echo: true
#| message: false
#| warning: false
#| fig-align: center
library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point(aes(color = factor(cyl)), size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "gray") +
  labs(
    title = "MPG vs Weight",
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  ) +
  theme_minimal()
```

## Dataset Summary Table
Here is the raw data preview utilizing our custom `.striped` and `.hover` table layouts.

```{r}
#| label: table-summary
#| echo: false
knitr::kable(head(mtcars), format = "markdown")
```
: Sample Data Overview {.striped .hover}
