---
title: "Quarto References"
format: 
    html:
        embed-resources: true
tbl-cap-location: bottom
---

# Tables

## Single Table
::: {.list-table}

- - header 1
  - header 2

- - row 1 col 1
  - row 1 col 2

- - row 2 col 1
  - row 2 col 2

:::

## Table with Caption and Reference

| fruit | price |
|-------|-------|
| apple | $1.00 |
| banana | $0.50 |

: Table 1: Fruit Prices {#tbl-fruit-prices}

See Table @tbl-fruit-prices for the prices of different fruits.


## Two Tables with Captions and References

::: {#tbl-panel layout-ncol=2}

| fruit | price |
|-------|-------|
| apple | $1.00 |
| banana | $0.50 |

: Table 1: Fruit Price {#tbl-fruits-price}

| item | price |
|-------|-------|
| Shirt | $10.50 |
| Pants | $20.00 |

: Table 2: Clothes Price {#tbl-clothes-price} 

References to the tables can be made using @tbl-fruits-price and @tbl-clothes-price in the Table Panel @tbl-panel

:::


## Embed Resources
format:
  html:
    embed-resources: true

quarto render report.qmd --to html --embed-resources


## R 
```{r}
#| label: tbl-mtcars-R
#| tbl-cap: "MTCars-R"
pacman::p_load(dplyr, knitr, gt, kableExtra, pander, flextable, tinytable, tinytex, reactable, DT)

data <- mtcars
cat("Table from R- Head\n")
head(data)
```

```{r}
#| label: tbl-mtcars-R-kable
#| tbl-cap: "MTCars-R-Kable"
#| results: "asis"
cat("Table from R- Kable \n")
print(kable(head(data)))
```

```{r}
#| label: tbl-mtcars-R-gt
#| tbl-cap: "MTCars-R-GT"
#| results: "asis"
cat("Table from R- GT\n")
data %>% head() %>% gt::gt()
```

```{r}
#| label: tbl-mtcars-R-kableExtra
#| tbl-cap: "MTCars-R-KableExtra"
#| results: "asis"
cat("Table from R- KableExtra\n")
#data %>% head() %>% kableExtra::kable_styling()
cat("Not working\n")
```

```{r}
#| label: tbl-mtcars-R-pander
#| tbl-cap: "MTCars-R-Pander"
#| results: "asis"
cat("Table from R- Pander\n")
pander(head(data))
```

```{r}
#| label: tbl-mtcars-R-flextable
#| tbl-cap: "MTCars-R-Flextable"
#| results: "asis"
cat("Table from R- Flextable\n")
flextable::flextable(head(data))
```

```{r}
cat("Table from R- Reactable\n")
reactable::reactable(head(data))
```

```{r}
cat("Table from R- DT\n")
DT::datatable(head(data))

#cat("Table from R- DT with options\n"  , DT::datatable(head(data), options = list(pageLength = 5, autoWidth = TRUE)))
```

```{r}
cat("Table from tinytable\n")
tinytable::tt(head(data))
```


## Python 
/Users/du/anaconda3/bin/python
Set the environment for Python code execution in Quarto. You can specify the path to your Python interpreter if needed.

```{python}
#| label: tbl-mtcars-P
#| tbl-cap: "MTCars-P"

from IPython.display import display, HTML, Markdown
from tabulate import tabulate
import pandas as pd
from pydataset import data
from great_tables import GT, md

data = data("mtcars")

print("Table from Python- Head\n")
data.head()

print("Table from Python- Tabulate\n")

Markdown(tabulate(data.head(), headers='keys', tablefmt='pipe'))

print("Table from Python- Markdown\n")

Markdown(data.head().to_markdown(index=False))

print("Table from Python- IPython display - HTML\n")
HTML(data.head().to_html(index=False))

print("Table from Python- Great Tables\n")
gt = GT(data.head())
gt

#(GT(gt).tab_header(title='Mtcars Data set'))

#from itables import show
#show(data.head())

```

Refer table from Python code using @tbl-mtcars-P and from R code using @tbl-mtcars-R