---
title: "Types of Dashboard in Quarto"
format: html
---
Quarto dashboards can be built in several styles depending on what you want: static reporting, interactive exploration, live apps, or multi-page analytical products.

**1. Static HTML Dashboard**

Good for reports that render once and are shared as HTML.

```yaml
---
title: "Sales Dashboard"
format:
  dashboard:
    embed-resources: true
---
```

Uses R/Python chunks, charts, tables, value boxes, etc. Interactivity can come from `plotly`, `DT`, `leaflet`, `reactable`, and similar widgets.

**2. Self-Contained Dashboard**

Same as above, but packaged into one HTML file.

```yaml
format:
  dashboard:
    embed-resources: true
```

Best for emailing or uploading a single file.

**3. Dashboard With Pages**

You can create multiple dashboard pages using top-level headings.

```markdown
# Executive Summary

## Row

# Category Analysis

## Row

# Data Table

## Row
```

Each `#` heading becomes a dashboard page/tab.

**4. Row/Column Layout Dashboard**

Use headings like `## Row` and `## Column` to control layout.

```markdown
# Overview

## Row

```{r}
# chart 1
```

```{r}
# chart 2
```

## Column

```{r}
# chart 3
```
```

**5. Dashboard With Value Boxes**

Good for KPI-style layouts.

```r
#| content: valuebox
list(
  title = "Sales",
  value = "$2.3M",
  icon = "cash-stack",
  color = "primary"
)
```

**6. Interactive Widget Dashboard**

Uses HTML widgets:

```r
plotly::ggplotly(p)
DT::datatable(df)
leaflet::leaflet()
reactable::reactable(df)
```

Good for filtering, tooltips, sorting, maps, and tables.

**7. Shiny Dashboard**

Good when you need live filters, reactive charts, user inputs, and server-side interactivity.

```yaml
---
title: "Interactive Sales Dashboard"
format: dashboard
server: shiny
---
```

Then use Shiny inputs:

```r
selectInput("region", "Region", choices = unique(df$Region))
plotOutput("sales_plot")
```

**8. Observable JS Dashboard**

Good for JavaScript-based interactive visualizations.

```yaml
---
title: "Observable Dashboard"
format: dashboard
---
```

Use Observable cells:

````markdown
```{ojs}
viewof category = Inputs.select(["Furniture", "Technology", "Office Supplies"])
```
````

**9. Python Dashboard**

Use Python chunks with `pandas`, `plotly`, `matplotlib`, `seaborn`, `great_tables`, etc.

```yaml
---
title: "Python Dashboard"
format: dashboard
jupyter: python3
---
```

```python
import pandas as pd
import plotly.express as px
```

**10. Multi-Format Dashboard**

You can define different output formats:

```yaml
format:
  dashboard:
    embed-resources: true
  html:
    toc: true
  typst:
    toc: true
```

But dashboard format is mainly for HTML.

**11. Website Dashboard**

You can include dashboards inside a Quarto website.

```yaml
project:
  type: website
```

Then pages like:

```text
index.qmd
dashboards/sales.qmd
dashboards/profit.qmd
```

**12. Parameterized Dashboard**

Useful for rendering the same dashboard for different regions, departments, or time periods.

```yaml
params:
  region: "West"
```

Then in R:

```r
df_region <- df |> filter(Region == params$region)
```

Render with:

```bash
quarto render dashboard.qmd -P region:West
```

Common choices:

- Simple shareable dashboard: static/self-contained dashboard
- Tableau-like dashboard: dashboard + `plotly` + `DT`
- True filter controls: Shiny dashboard
- JavaScript-heavy interactive dashboard: Observable dashboard
- Reusable regional dashboards: parameterized dashboard
- Portfolio/reporting hub: Quarto website with dashboard pages

## Links to share

[https://learning.nceas.ucsb.edu/2024-03-ucsb-faculty/session_10.html](https://learning.nceas.ucsb.edu/2024-03-ucsb-faculty/session_10.html)
